---
title: "Statistical Inference Part 1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

In this project we are doing a simulation exercise. 

We will be investigating the exponential distribution in R and comparing it with the Central Limit Theorem by analysing the distribution of averages of 40 exponentials, and doing 1,000 simulations.

## Simulations

The code below simulates 40 exponentials x happening at rate lambda = 0.2: 
```{r}
set.seed(123)
x <- rexp(40, 0.2)
hist(x)
```

To carry out the bootstrap principle, we will sample 40 (n) obvervations with replacement from the observed data 1,000 times (B), and take the mean of each data set.

```{r}
B <- 1000
n <- length(x)
resamples <- matrix(sample(x, n*B, replace=TRUE), B, n)
means <- apply(resamples, 1, mean)
```

This is approximately like drawing from the sampling distribution of that statistic.

## Sample Mean versus Theoretical Mean

This is the sampling distribution of the mean using the bootstrap (black line), compared to the theorerical mean of an exponential distribution 1/lambda (blue line).

```{r}
library(ggplot2)
g <- ggplot(data.frame(x = means), aes(x = x))
g <- g + geom_density( fill = "yellow")
g <- g + geom_vline(xintercept = 1/0.2, size = 1, colour = "blue")
g <- g + geom_vline(xintercept = mean(means), size = 1, colour = "black")
g <- g + ggtitle("Bootstrap: Sampling Distribution of the Mean vs Theorical Mean")
g
```

Sample mean:
```{r}
sample_mean <- mean(means)
sample_mean
```

Theorical mean:
```{r}
theoretical_mean <- 1/0.2
theoretical_mean
```

## Sample Variance versus Theoretical Variance

Our sample mean has variance 0.42, compared to our theorical mean (1 / lambda)^2 / (n) = 0.62.

```{r}
sample_var<- var(means)
sample_var
```

```{r}
theoretical_var  <- (1 / 0.2)^2 /40 
theoretical_var
```

Our sample mean has a standard deviation of 0.65, compared to our theorical standard devatino of 0.79:

```{r}
sample_sd <- sd(means)
sample_sd
```

```{r}
theoretical_sd  <- 1 / (0.2 * sqrt(40))
theoretical_sd
```

## Distribution

The distribution of sample means (black) is close to the distribution of the theorical mean (blue) given the value of lambda = 0.2.

```{r}
m <- g + stat_function(fun = dnorm, args = list(mean = mean(means), sd = sd(means)), color = "black", size = 1.0)
m <- m + stat_function(fun = dnorm, args = list(mean = 1/0.2, sd = 1 / (0.2 * sqrt(40))), colour = "blue", size = 1.0)
m
```



